### 2021-12-08 input/proposal.tex
proposal for last

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. A \process $s$ that performs a
\texttt{Del} operation implicitly states that all its preceding
\texttt{Add} operations become obsolete. As consequence, their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications $\delta_s$.

@@

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest broadcast of a \node matters.  A message $m$ conveys
  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
  \process only sends messages that it assumes
  \underline{u}p-\underline{t}o-\underline{d}ate.
  % : $s_x(\alpha_s)
  % \implies \delta_s \not\in R_x$.
  For convenience, we define $\textup{minUTD(}D\textup{)} = \min
  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$.
  %  \TODO{Only keep last?  Tothink what happens if we keep all as in
%    def now.}
\end{definition}

@@

\begin{definition}[\label{def:fs}\underline{F}orwarding of
    \underline{s}taleness (FS)]
  %
  A \process $x$ delivers and forwards a received staleness
  notification if it targets its best up-to-date delivered message:
  $(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.
\end{definition}

>>>>

Delete operations bring a new notion of order between events, and most
importantly between message deliveries. A \process $s$ that performs a
\texttt{Del} operation implicitly states that all its preceding
\texttt{Add} operations become obsolete. As consequence, their results
-- scoped broadcast in the form of \texttt{\underline{A}dd}
notifications $\alpha_s$ -- should be canceled by the corresponding
\texttt{\underline{D}el} notifications $\delta_s$. \TODO{From algo, we
  see that last is also best, so we want to exploit this. but why ? or
  should we show ``forwarding all staleness'' first.}

@@

\begin{definition}[\label{def:lwo}Stale messages]
  Only the latest broadcast of a \node matters.  A message $m$ conveys
  \underline{s}tale control information $\mathcal{S}(m)$ as soon as
  its broadcaster broadcasts another message: $\mathcal{S}(\alpha_x) =
  \exists \delta_x: b_x(\alpha_x) \rightarrow b_x(\delta_x)$.  A
  \process only delivers or sends messages that it assumes
  \underline{u}p-\underline{t}o-\underline{d}ate.
  % : $s_x(\alpha_s)
  % \implies \delta_s \not\in R_x$.
  For convenience, we define $\textup{minUTD(}D\textup{)} = \min
  \{\alpha_s^d | \alpha_s^d \in D \wedge \delta_s \notin D\}$, and
  $\textup{last(}D\textup{)} = \alpha_s \in D: \nexists \alpha_{s'}
  \in D: d_x(\alpha_s) \rightarrow d_x(\alpha_{s'})$.
  %  \TODO{Only keep last?  Tothink what happens if we keep all as in
%    def now.}
\end{definition}

@@

\begin{definition}[\label{def:fs}\underline{F}orwarding of
    \underline{s}taleness (FS)]
  %
  A \process $x$ delivers and forwards a received staleness
  notification if it targets its best up-to-date delivered message:\\
  \TODO{$(\delta_s \in R_x \wedge \alpha_s = \textup{minUTD}~D_x) \iff
  \eventually (d_x(\delta_s) \rightarrow f_x(\delta_s))$.}\\
  $\textup{last}~D = \alpha_s \wedge d_x(\alpha_s) \rightarrow r_x(\delta_s)
  \implies d_x(\delta_s) \rightarrow f_x(\delta_s)$.
\end{definition}
